Mbh-n paper

### 2015-11-04 papers/mbhn/mbhn.tex
wed

The S\'ersic model parametrizes the intensity $I$ as a function of the projected galactic radius $R$ such that

@@

but they surprisingly failed to recover a strong $M_{\rm BH} - n_{\rm sph}$ relation. 

@@

This was suggestive that the individual galaxy decompositions of \cite{sani2011}, \cite{vika2012} and \cite{beifiori2012} were not accurate, 

@@

In this Paper (\emph{Paper III}) we focus on the $M_{\rm BH} - n_{\rm sph}$ relation. \\
This paper is structured as follows...

\section{Data}
We populated the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams 
with the same galaxy sample (Table \ref{tab:sample}) used in \emph{Paper II}, 
i.e.~66 galaxies for which a dynamical measurement of the black hole mass has been reported in the literature 
(by \citealt{grahamscott2013} or \citealt{rusli2013}) 
and for which we were able to successfully model the light distribution and measure the spheroid structural parameters 
using $3.6\rm~\mu m$ \emph{Spitzer} satellite images. 
Our galaxy decompositions take into account bulge, disks, spiral arms, bars, rings, halo, 
extended or unresolved nuclear source and partially depleted core, 
and -- for the first time -- they were checked to be consistent with the galaxy kinematics 
\citep{atlas3dIII,scott2014,arnold2014}. 
Kinematical information was used to confirm the presence of disk components 
in the majority of early-type (elliptical + lenticular) galaxies and, more importantly,  
to estabilish the radial extent of these disks, 
which in most cases is not obvious from a visual inspection of the galaxy images. 
This enabled us to distinguish between intermediate-scale disks, 
that are fully embedded in the spheroid,  
and large-scale disks, that encase the bulge and dominate the light at large radii.  
Savorgnan \& Graham (2015) explain that when an intermediate-scale disk is misclassified and modeled as a large-scale disk, 
the luminosity of the spheroid is underestimated, 
hence the galaxy incorrectly appears as a positive outlier (an ``over-massive'' black hole) in the $M_{\rm BH} - L_{\rm sph}$ diagram. 
A detailed description of the dataset used here, the data reduction process and the galaxy modelling technique that we developed 
can be found in \emph{Paper I}, 
along with a discussion of how we estimated the uncertainties on the spheroid S\'ersic indices\footnote{The uncertainties associated with 
the spheroid S\'ersic indices have been estimated with a method that takes into account systematic errors. 
This method consists in comparing, for each of our galaxies, the measurements of the spheroid S\'ersic index obtained by different studies 
with that obtained by us. 
Systematic errors are typically not considered by popular 2D fitting codes which report only the statistical errors 
associated with their fitted parameters. 
Refer to \emph{Paper I} for a detailed discussion on this. }.  
The morphological classification (E = elliptical; E/S0 = elliptical/lenticular; S0 = lenticular; 
S0/Sp = lenticular/spiral; Sp = spiral; and ``merger'') follows from the galaxy decompositions illustrated in \emph{Paper I}. 
As in \emph{Paper II}, here we will refer to early-type galaxies (E+S0) and late-type galaxies (Sp). 
The early-type bin includes two galaxies classified as E/S0, 
whereas two galaxies classified as S0/Sp and another two classified as mergers are included in neither the early- nor the late-type bin.

@@

\section{Analysis and results}
As in \emph{Paper II}, a linear regression analysis of the $L_{\rm sph} - n_{\rm sph}$ 
and $M_{\rm BH} - n_{\rm sph}$ diagrams (see Table \ref{tab:lregLn} and Table \ref{tab:lregMn}, respectively) 
was performed using three different routines: 
the BCES code from \cite{akritasbershady1996}, 
the FITEXY routine \citep{press1992}, as modified by \cite{tremaine2002}, 
and the Bayesian estimator {\tt linmix\_err} \citep{linmixerr}.
All of these three routines take into account the intrinsic scatter, 
but only the FITEXY and the {\tt linmix\_err} codes allow one to quantify it.
We report both symmetrical and nonsymmetrical linear regressions.  
Symmetrical regressions are meant to be compared with theoretical expectations, 
whereas nonsymmetrical forward ($Y|X$) regressions -- which minimize the scatter in the $Y$ direction -- 
allow one to predict values of the ordinate observable ($Y$) with the best possible precision.

%for different morphological types (elliptical/lenticular/spiral)

\subsection{$L_{\rm sph} - n_{\rm sph}$}

@@

\subsection{$M_{\rm BH} - n_{\rm sph}$}

@@

@@

Elliptical (30)	       & BCES $(Y|X)$		    & $-25.46 \pm 1.12$ & $38.47 \pm 114.45$ & $0.76$ & $-$ & $6.37$ \\
		       & mFITEXY $(Y|X)$	    & $-25.74 \pm 0.18$ & $-9.74 \pm 1.59$ & $0.76$ & $0.24^{+0.32}_{-0.24}$ & $0.94$ \\
		       & {\tt linmix\_err} $(Y|X)$  & $-25.65 \pm 0.21$ & $-7.87 \pm 2.15$ & $0.76$ & $0.61 \pm 0.22$ & $1.06$ \\ [0.5em]
		       & BCES $(X|Y)$		    & $-25.46 \pm 0.23$ & $-10.73 \pm 3.21$ & $0.76$ & $-$ & $1.29$ \\
		       & mFITEXY $(X|Y)$	    & $-25.74 \pm 0.20$ & $-10.42 \pm 1.79$ & $0.76$ & $0.22^{+0.38}_{-0.22}$ & $1.29$ \\
		       & {\tt linmix\_err} $(X|Y)$  & $-25.72 \pm 0.28$ & $-10.92 \pm 2.70$ & $0.76$ & $0.73 \pm 0.34$ & $1.33$ \\ [0.5em]
		       & BCES Bisector  	    & $-25.46 \pm 0.20$ & $0.03 \pm 0.05$ & $0.76$ & $-$ & $1.14$ \\
		       & mFITEXY Bisector	    & $-25.74 \pm 0.19$ & $-10.07 \pm 1.19$ & $0.76$ & $-$ & $1.26$ \\
		       & {\tt linmix\_err} Bisector & $-25.68 \pm 0.25$ & $-9.15 \pm 1.74$ & $0.76$ & $-$ & $1.16$ \\ [0.5em]

Lenticular (11)	       & BCES $(Y|X)$		    & $-22.08 \pm 1.66$ & $33.52 \pm 98.87$ & $0.33$ & $-$ & $6.09$ \\
		       & mFITEXY $(Y|X)$	    & $-22.11 \pm 0.24$ & $-6.31 \pm 2.45$ & $0.33$ & $0.42^{+0.28}_{-0.17}$ & $0.71$ \\
		       & {\tt linmix\_err} $(Y|X)$  & $$ & $$ & $0.33$ & $$ & $$ \\ [0.5em]
		       & BCES $(X|Y)$		    & $-22.08 \pm 0.19$ & $-6.83 \pm 1.16$ & $0.33$ & $-$ & $0.71$ \\
		       & mFITEXY $(X|Y)$	    & $-21.94 \pm 0.44$ & $-13.16 \pm 7.91$ & $0.33$ & $0.61^{+0.60}_{-0.56}$ & $1.39$ \\
		       & {\tt linmix\_err} $(X|Y)$  & $$ & $$ & $0.33$ & $$ & $$ \\ [0.5em]
		       & BCES Bisector  	    & $-22.08 \pm 0.30$ & $0.06 \pm 0.05$ & $0.33$ & $-$ & $1.09$ \\
		       & mFITEXY Bisector	    & $-22.05 \pm 0.35$ & $-8.55 \pm 2.79$ & $0.33$ & $-$ & $0.84$ \\
		       & {\tt linmix\_err} Bisector & $$ & $$ & $0.33$ & $-$ & $$ \\ [0.5em]

Spiral (17)	       & BCES $(Y|X)$		    & $-22.33 \pm 0.26$ & $-5.31 \pm 5.83$ & $0.18$ & $-$ & $1.15$ \\
		       & mFITEXY $(Y|X)$	    & $-22.22 \pm 0.19$ & $-2.17 \pm 0.98$ & $0.18$ & $0.53^{+0.24}_{-0.13}$ & $0.72$ \\
		       & {\tt linmix\_err} $(Y|X)$  & $-22.26 \pm 0.24$ & $-1.53 \pm 1.88$ & $0.18$ & $0.71 \pm      0.22$ & $0.78$ \\ [0.5em]
		       & BCES $(X|Y)$		    & $-22.33 \pm 0.26$ & $-5.19 \pm 3.77$ & $0.18$ & $-$ & $1.13$ \\
		       & mFITEXY $(X|Y)$	    & $-22.28 \pm 0.44$ & $-9.08 \pm 5.31$ & $0.51$ & $1.12^{+0.54}_{-0.31}$ & $1.83$ \\
		       & {\tt linmix\_err} $(X|Y)$  & $-22.24 \pm 0.71$ & $-11.12 \pm 13.59$ & $0.18$ & $1.95 \pm 2.47$ & $2.24$ \\ [0.5em]
		       & BCES Bisector  	    & $-22.33 \pm 0.26$ & $-5.25 \pm 3.38$ & $0.18$ & $-$ & $1.14$ \\
		       & mFITEXY Bisector	    & $-22.23 \pm 0.33$ & $-3.60 \pm 1.29$ & $0.18$ & $-$ & $0.92$ \\
		       & {\tt linmix\_err} Bisector & $-22.25 \pm 0.53$ & $-2.88 \pm 2.66$ & $0.18$ & $-$ & $0.84$ \\ [0.5em]

@@

\begin{table*}
\centering
\caption{Linear regression analysis of the $L_{\rm sph} - n_{\rm sph}$ diagram.}
\begin{tabular}{llccccc}
\tableline
\tableline
{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle \log n_{\rm sph} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
\tableline 
\\
Early-type (43)	       & BCES $(Y|X)$		    & $-24.55 \pm 0.22$ & $-11.84 \pm 2.29$ & $0.64$ & $-$ & $1.50$ \\
		       & mFITEXY $(Y|X)$	    & $-24.74 \pm 0.14$ & $-8.86 \pm 0.66$ & $0.51$ & $0.27^{+0.20}_{-0.27}$ & $0.87$ \\
		       & {\tt linmix\_err} $(Y|X)$  & $-24.70 \pm 0.17$ & $-8.28 \pm 0.87$ & $0.64$ & $0.58 \pm 0.17$ & $0.98$ \\ [0.5em]
		       & BCES $(X|Y)$		    & $-24.55 \pm 0.14$ & $-8.25 \pm 0.63$ & $0.64$ & $-$ & $0.96$ \\
		       & mFITEXY $(X|Y)$	    & $-24.74 \pm 0.14$ & $-9.13 \pm 0.68$ & $0.64$ & $0.23^{+0.25}_{-0.23}$ & $1.08$ \\
		       & {\tt linmix\_err} $(X|Y)$  & $-24.73 \pm 0.18$ & $-9.08 \pm 0.87$ & $0.64$ & $0.60 \pm 0.21$ & $1.07$ \\ [0.5em]
		       & BCES Bisector  	    & $-24.55 \pm 0.17$ & $-9.73 \pm 1.05$ & $0.64$ & $-$ & $1.14$ \\
		       & mFITEXY Bisector	    & $-24.74 \pm 0.14$ & $-8.99 \pm 0.48$ & $0.64$ & $-$ & $1.06$ \\
		       & {\tt linmix\_err} Bisector & $-24.72 \pm 0.17$ & $-8.66 \pm 0.63$ & $0.64$ & $-$ & $1.02$ \\ [0.5em]

Bulge  (30)	       & BCES $(Y|X)$		    & $-22.25 \pm 0.20$ & $-5.88 \pm 3.06$ & $0.26$ & $-$ & $1.16$ \\
		       & mFITEXY $(Y|X)$	    & $-22.19 \pm 0.14$ & $-2.99 \pm 0.73$ & $0.26$ & $0.52^{+0.18}_{-0.10}$ & $0.75$ \\
		       & {\tt linmix\_err} $(Y|X)$  & $-22.20 \pm 0.17$ & $-2.48 \pm 1.21$ & $0.26$ & $0.67 \pm 0.15$ & $0.83$ \\ [0.5em]
		       & BCES $(X|Y)$		    & $-22.25 \pm 0.20$ & $-5.85 \pm 1.83$ & $0.26$ & $-$ & $1.15$ \\
		       & mFITEXY $(X|Y)$	    & $-22.17 \pm 0.25$ & $-7.65 \pm 2.43$ & $0.26$ & $0.87^{+0.30}_{-0.18}$ & $1.46$ \\
		       & {\tt linmix\_err} $(X|Y)$  & $-22.16 \pm 0.31$ & $-7.80 \pm 3.89$ & $0.26$ & $1.18 \pm 0.65$ & $1.48$ \\ [0.5em]
		       & BCES Bisector  	    & $-22.25 \pm 0.20$ & $-5.87 \pm 2.06$ & $0.26$ & $-$ & $1.16$ \\
		       & mFITEXY Bisector	    & $-22.18 \pm 0.20$ & $-4.34 \pm 0.84$ & $0.26$ & $-$ & $0.96$ \\
		       & {\tt linmix\_err} Bisector & $-22.19 \pm 0.25$ & $-3.83 \pm 1.39$ & $0.26$ & $-$ & $0.91$ \\ [1.0em]

@@

 Elliptical (30)	& BCES $(Y|X)$  	     & $8.80 \pm 0.53$ & $-18.16 \pm 53.99$ & $0.76$ & $-$ & $3.02$ \\
 			& mFITEXY $(Y|X)$	     & $8.90 \pm 0.10$ & $4.47 \pm 0.88$ & $0.76$ & $0.29^{+0.14}_{-0.10}$ & $0.56$ \\
 			& {\tt linmix\_err} $(Y|X)$  & $8.84 \pm 0.12$ & $3.56 \pm 1.35$ & $0.76$ & $0.44 \pm 0.12$ & $0.59$ \\ [0.5em]
 			& BCES $(X|Y)$  	     & $8.80 \pm 0.18$ & $8.00 \pm 2.55$ & $0.76$ & $-$ & $1.01$ \\
 			& mFITEXY $(X|Y)$	     & $8.92 \pm 0.15$ & $6.85 \pm 1.75$ & $0.76$ & $0.36^{+0.20}_{-0.15}$ & $0.89$ \\
 			& {\tt linmix\_err} $(X|Y)$  & $8.89 \pm 0.20$ & $6.96 \pm 2.49$ & $0.76$ & $0.63 \pm 0.30$ & $0.89$ \\ [0.5em]
 			& BCES Bisector 	     & $8.80 \pm 0.11$ & $-0.03 \pm 0.10$ & $0.76$ & $-$ & $0.64$ \\
 			& mFITEXY Bisector	     & $8.91 \pm 0.13$ & $5.42 \pm 0.85$ & $0.76$ & $-$ & $0.73$ \\
 			& {\tt linmix\_err} Bisector & $8.85 \pm 0.16$ & $4.73 \pm 1.30$ & $0.76$ & $-$ & $0.67$ \\ [0.5em]

 Lenticular (11)	& BCES $(Y|X)$  	     & $7.75 \pm 0.58$ & $-11.51 \pm 31.78$ & $0.33$ & $-$ & $2.11$ \\
 			& mFITEXY $(Y|X)$	     & $7.65 \pm 0.12$ & $3.78 \pm 1.20$ & $0.33$ & $0.00^{+0.00}_{-0.00}$ & $0.26$ \\
 			& {\tt linmix\_err} $(Y|X)$  & $$ & $$ & $0.33$ & $$ & $$ \\ [0.5em]
 			& BCES $(X|Y)$  	     & $7.75 \pm 0.13$ & $3.54 \pm 0.99$ & $0.33$ & $-$ & $0.46$ \\
 			& mFITEXY $(X|Y)$	     & $7.65 \pm 0.12$ & $3.78 \pm 1.20$ & $0.33$ & $0.00^{+0.00}_{-0.00}$ & $0.49$ \\
 			& {\tt linmix\_err} $(X|Y)$  & $$ & $$ & $0.33$ & $$ & $$ \\ [0.5em]
 			& BCES Bisector 	     & $7.75 \pm 0.13$ & $-0.09 \pm 0.15$ & $0.33$ & $-$ & $0.48$ \\
 			& mFITEXY Bisector	     & $7.65 \pm 0.12$ & $3.78 \pm 0.85$ & $0.33$ & $-$ & $0.49$ \\
 			& {\tt linmix\_err} Bisector & $$ & $$ & $0.33$ & $-$ & $$ \\ [0.5em]

>>>>

The S\'ersic model parametrizes the intensity of light $I$ as a function of the projected galactic radius $R$ such that

@@

but they unexpectedly failed to recover a strong $M_{\rm BH} - n_{\rm sph}$ relation. 

@@

This was suggesting that the individual galaxy decompositions of \cite{sani2011}, \cite{vika2012} and \cite{beifiori2012} were not accurate, 

@@

Here we focus on the $M_{\rm BH} - n_{\rm sph}$ relation. \\
This paper (\emph{Paper III}) is structured as follows...

\section{Data}
We populated the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams 
with the same galaxy sample (Table \ref{tab:sample}) used in \emph{Paper II}, 
i.e.~66 galaxies for which a dynamical measurement of the black hole mass has been reported in the literature 
(by \citealt{grahamscott2013} or \citealt{rusli2013}) 
and for which we were able to successfully model the light distribution and measure the spheroid structural parameters 
using $3.6\rm~\mu m$ \emph{Spitzer} satellite images. 
Our galaxy decompositions take into account bulge, disks, spiral arms, bars, rings, halo, 
extended or unresolved nuclear source and partially depleted core, 
and -- for the first time -- they were checked to be consistent with the galaxy kinematics 
\citep{atlas3dIII,scott2014,arnold2014}. 
Kinematical information was used to confirm the presence of disk components 
in the majority of early-type (elliptical + lenticular) galaxies and, more importantly,  
to estabilish the radial extent of these disks, 
which in most cases is not obvious from a visual inspection of the galaxy images. 
This enabled us to distinguish between intermediate-scale disks, 
that are fully embedded in the spheroid,  
and large-scale disks, that encase the bulge and dominate the light at large radii.  
Savorgnan \& Graham (2015) explain that when an intermediate-scale disk is misclassified and modeled as a large-scale disk, 
the luminosity of the spheroid is underestimated, 
hence the galaxy incorrectly appears as a positive outlier (an ``over-massive'' black hole) in the $M_{\rm BH} - L_{\rm sph}$ diagram. 
A detailed description of the dataset used here, the data reduction process and the galaxy modelling technique that we developed 
can be found in \emph{Paper I}, 
along with a discussion of how we estimated the uncertainties on the spheroid S\'ersic indices\footnote{The uncertainties associated with 
the spheroid S\'ersic indices have been estimated with a method that takes into account systematic errors. 
This method consists in comparing, for each of our galaxies, the measurements of the spheroid S\'ersic index obtained by different studies 
with that obtained by us. 
Systematic errors are typically not considered by popular 2D fitting codes which report only the statistical errors 
associated with their fitted parameters. 
Refer to \emph{Paper I} for a detailed discussion on this. }.  
The morphological classification (E = elliptical; E/S0 = elliptical/lenticular; S0 = lenticular; 
S0/Sp = lenticular/spiral; Sp = spiral; and ``merger'') follows from the galaxy decompositions illustrated in \emph{Paper I}. 
As in \emph{Paper II}, we will refer to early-type galaxies (E+S0) and late-type galaxies (Sp). 
The early-type bin includes the two galaxies classified as E/S0, 
whereas the two galaxies classified as S0/Sp and the two galaxies classified as mergers are included in neither the early- nor the late-type bin.

@@

\section{Analysis and results}
As in \emph{Paper II}, a linear regression analysis of the $L_{\rm sph} - n_{\rm sph}$ 
(Table \ref{tab:lregLn} and Figure \ref{fig:magn})
and $M_{\rm BH} - n_{\rm sph}$ (Table \ref{tab:lregMn} and Figure \ref{fig:mbhn}) diagrams 
was performed using three different routines: 
the BCES code from \cite{akritasbershady1996}, 
the FITEXY routine \citep{press1992}, as modified by \cite{tremaine2002}, 
and the Bayesian estimator {\tt linmix\_err} \citep{linmixerr}.
All of these three routines take into account the intrinsic scatter, 
but only the FITEXY and the {\tt linmix\_err} codes allow one to quantify it.
We report both symmetrical and nonsymmetrical linear regressions.  
Symmetrical regressions are meant to be compared with theoretical expectations, 
whereas nonsymmetrical forward ($Y|X$) regressions -- which minimize the scatter in the $Y$ direction -- 
allow one to predict the value of the observable $Y$ with the best possible precision. \\
We searched for extreme outliers in both the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams, 
and found that in our $L_{\rm sph} - n_{\rm sph}$ plot there are no $3\sigma$ outliers, 
whereas in our $M_{\rm BH} - n_{\rm sph}$ plot 
the S0 galaxies NGC 0524 and NGC 3998 reside more than $3\sigma$ from the bisector linear regression for all galaxies. 
These two galaxies have therefore been excluded from the rest of the analysis. \\
{\bf fitexy does better job, we report that} \\

\subsection{$L_{\rm sph} - n_{\rm sph}$}
Following \cite{graham2001}, 
who showed that the $L_{\rm sph} - n_{\rm sph}$ relation is different for elliptical galaxies and the bulges of disk galaxies (S0+Sp), 
\cite{savorgnan2013} re-analyzed the data from \cite{grahamguzman2003} and \cite{graham2013} 
and obtained two separate $L_{\rm sph} - n_{\rm sph}$ symmetrical linear regressions for elliptical galaxies and the bulges of disk galaxies 
(in the B- and K-band, respectively). 
At the time, the $L_{\rm sph} - n_{\rm sph}$ datasets from \cite{grahamguzman2003} and \cite{graham2013} were of the best quality available 
to investigate the $L_{\rm sph} - n_{\rm sph}$ relation for different galaxy morphological types. 
However, these datasets were not the output of a homogeneous analysis, 
but the collection of the results from various past bulge/disk decomposition studies. 
It is also worth mentioning that, 
although the K-band luminosities of the bulges of disk galaxies had been corrected for internal dust absorption, 
{\bf the dust corrections are not precise today refs??, imagine at the time.....}  
Here we re-investigate the $L_{\rm sph} - n_{\rm sph}$ diagram with our top-quality dataset  
derived from our state-of-the-art multicomponent galaxy decompositions, 
that were performed in a consistent manner 
and using the $3.6\rm~\mu m$ band, which is less affected by dust extinction than the K-band. \\
The values of the slope and intercept of the bisector linear regression for the lenticular galaxies 
are not consistent within the errors with those for the spiral galaxies, 
but are consistent within the errors with those for the elliptical galaxies.  
Given this, we conclude that in the $L_{\rm sph} - n_{\rm sph}$ diagram 
elliptical and lenticular galaxies form together a single sequence, 
whereas the combination of lenticular and spiral galaxies do not. 
{\bf why?? dust? multicomponent? classification?}

ell and s0 have same slope -> early seq \\
different from late seq \\

@@

\subsection{$M_{\rm BH} - n_{\rm sph}$}
in sav13 we had m-l from gs13 for core sersic and sersic \\
however in paper II we say that this is not the case, there are red and blue seq \\
therefore we look for red and blue seq here \\
consistent with each other \\

@@

\section{Discussion}
intr scatter of correlation for all?\\
data suggest that m-n more fundamental than l-n ? \\

@@

Elliptical (E) (30)    & BCES $(Y|X)$		    & $-25.46 \pm 1.12$ & $38.47 \pm 114.45$ & $0.76$ & $-$ & $6.37$ \\
		       & mFITEXY $(Y|X)$	    & $-25.74 \pm 0.18$ & $-9.74 \pm 1.59$ & $0.76$ & $0.24^{+0.32}_{-0.24}$ & $0.94$ \\
		       & {\tt linmix\_err} $(Y|X)$  & $-25.65 \pm 0.21$ & $-7.87 \pm 2.15$ & $0.76$ & $0.61 \pm 0.22$ & $1.06$ \\ [0.5em]
		       & BCES $(X|Y)$		    & $-25.46 \pm 0.23$ & $-10.73 \pm 3.21$ & $0.76$ & $-$ & $1.29$ \\
		       & mFITEXY $(X|Y)$	    & $-25.74 \pm 0.20$ & $-10.42 \pm 1.79$ & $0.76$ & $0.22^{+0.38}_{-0.22}$ & $1.29$ \\
		       & {\tt linmix\_err} $(X|Y)$  & $-25.72 \pm 0.28$ & $-10.92 \pm 2.70$ & $0.76$ & $0.73 \pm 0.34$ & $1.33$ \\ [0.5em]
		       & BCES Bisector  	    & $-25.46 \pm 0.20$ & $0.03 \pm 0.05$ & $0.76$ & $-$ & $1.14$ \\
		       & mFITEXY Bisector	    & $-25.74 \pm 0.19$ & $-10.07 \pm 1.19$ & $0.76$ & $-$ & $1.26$ \\
		       & {\tt linmix\_err} Bisector & $-25.68 \pm 0.25$ & $-9.15 \pm 1.74$ & $0.76$ & $-$ & $1.16$ \\ [0.5em]

Lenticular (S0) (11)   & BCES $(Y|X)$		    & $-22.08 \pm 1.66$ & $33.52 \pm 98.87$ & $0.33$ & $-$ & $6.09$ \\
		       & mFITEXY $(Y|X)$	    & $-22.11 \pm 0.24$ & $-6.31 \pm 2.45$ & $0.33$ & $0.42^{+0.28}_{-0.17}$ & $0.71$ \\
		       & {\tt linmix\_err} $(Y|X)$  & $$ & $$ & $0.33$ & $$ & $$ \\ [0.5em]
		       & BCES $(X|Y)$		    & $-22.08 \pm 0.19$ & $-6.83 \pm 1.16$ & $0.33$ & $-$ & $0.71$ \\
		       & mFITEXY $(X|Y)$	    & $-21.94 \pm 0.44$ & $-13.16 \pm 7.91$ & $0.33$ & $0.61^{+0.60}_{-0.56}$ & $1.39$ \\
		       & {\tt linmix\_err} $(X|Y)$  & $$ & $$ & $0.33$ & $$ & $$ \\ [0.5em]
		       & BCES Bisector  	    & $-22.08 \pm 0.30$ & $0.06 \pm 0.05$ & $0.33$ & $-$ & $1.09$ \\
		       & mFITEXY Bisector	    & $-22.05 \pm 0.35$ & $-8.55 \pm 2.79$ & $0.33$ & $-$ & $0.84$ \\
		       & {\tt linmix\_err} Bisector & $$ & $$ & $0.33$ & $-$ & $$ \\ [0.5em]

Spiral (Sp) (17)       & BCES $(Y|X)$		    & $-22.33 \pm 0.26$ & $-5.31 \pm 5.83$ & $0.18$ & $-$ & $1.15$ \\
		       & mFITEXY $(Y|X)$	    & $-22.22 \pm 0.19$ & $-2.17 \pm 0.98$ & $0.18$ & $0.53^{+0.24}_{-0.13}$ & $0.72$ \\
		       & {\tt linmix\_err} $(Y|X)$  & $-22.26 \pm 0.24$ & $-1.53 \pm 1.88$ & $0.18$ & $0.71 \pm      0.22$ & $0.78$ \\ [0.5em]
		       & BCES $(X|Y)$		    & $-22.33 \pm 0.26$ & $-5.19 \pm 3.77$ & $0.18$ & $-$ & $1.13$ \\
		       & mFITEXY $(X|Y)$	    & $-22.28 \pm 0.44$ & $-9.08 \pm 5.31$ & $0.51$ & $1.12^{+0.54}_{-0.31}$ & $1.83$ \\
		       & {\tt linmix\_err} $(X|Y)$  & $-22.24 \pm 0.71$ & $-11.12 \pm 13.59$ & $0.18$ & $1.95 \pm 2.47$ & $2.24$ \\ [0.5em]
		       & BCES Bisector  	    & $-22.33 \pm 0.26$ & $-5.25 \pm 3.38$ & $0.18$ & $-$ & $1.14$ \\
		       & mFITEXY Bisector	    & $-22.23 \pm 0.33$ & $-3.60 \pm 1.29$ & $0.18$ & $-$ & $0.92$ \\
		       & {\tt linmix\_err} Bisector & $-22.25 \pm 0.53$ & $-2.88 \pm 2.66$ & $0.18$ & $-$ & $0.84$ \\ [0.5em]

@@

\begin{table*}
\centering
\caption{Linear regression analysis of the $L_{\rm sph} - n_{\rm sph}$ diagram.}
\begin{tabular}{llccccc}
\tableline
\tableline
{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle \log n_{\rm sph} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
\tableline 
\\
Early-type (E+S0) (43) & BCES $(Y|X)$		    & $-24.55 \pm 0.22$ & $-11.84 \pm 2.29$ & $0.64$ & $-$ & $1.50$ \\
		       & mFITEXY $(Y|X)$	    & $-24.74 \pm 0.14$ & $-8.86 \pm 0.66$ & $0.51$ & $0.27^{+0.20}_{-0.27}$ & $0.87$ \\
		       & {\tt linmix\_err} $(Y|X)$  & $-24.70 \pm 0.17$ & $-8.28 \pm 0.87$ & $0.64$ & $0.58 \pm 0.17$ & $0.98$ \\ [0.5em]
		       & BCES $(X|Y)$		    & $-24.55 \pm 0.14$ & $-8.25 \pm 0.63$ & $0.64$ & $-$ & $0.96$ \\
		       & mFITEXY $(X|Y)$	    & $-24.74 \pm 0.14$ & $-9.13 \pm 0.68$ & $0.64$ & $0.23^{+0.25}_{-0.23}$ & $1.08$ \\
		       & {\tt linmix\_err} $(X|Y)$  & $-24.73 \pm 0.18$ & $-9.08 \pm 0.87$ & $0.64$ & $0.60 \pm 0.21$ & $1.07$ \\ [0.5em]
		       & BCES Bisector  	    & $-24.55 \pm 0.17$ & $-9.73 \pm 1.05$ & $0.64$ & $-$ & $1.14$ \\
		       & mFITEXY Bisector	    & $-24.74 \pm 0.14$ & $-8.99 \pm 0.48$ & $0.64$ & $-$ & $1.06$ \\
		       & {\tt linmix\_err} Bisector & $-24.72 \pm 0.17$ & $-8.66 \pm 0.63$ & $0.64$ & $-$ & $1.02$ \\ [0.5em]

Bulge (S0+Sp) (30)     & BCES $(Y|X)$		    & $-22.25 \pm 0.20$ & $-5.88 \pm 3.06$ & $0.26$ & $-$ & $1.16$ \\
		       & mFITEXY $(Y|X)$	    & $-22.19 \pm 0.14$ & $-2.99 \pm 0.73$ & $0.26$ & $0.52^{+0.18}_{-0.10}$ & $0.75$ \\
		       & {\tt linmix\_err} $(Y|X)$  & $-22.20 \pm 0.17$ & $-2.48 \pm 1.21$ & $0.26$ & $0.67 \pm 0.15$ & $0.83$ \\ [0.5em]
		       & BCES $(X|Y)$		    & $-22.25 \pm 0.20$ & $-5.85 \pm 1.83$ & $0.26$ & $-$ & $1.15$ \\
		       & mFITEXY $(X|Y)$	    & $-22.17 \pm 0.25$ & $-7.65 \pm 2.43$ & $0.26$ & $0.87^{+0.30}_{-0.18}$ & $1.46$ \\
		       & {\tt linmix\_err} $(X|Y)$  & $-22.16 \pm 0.31$ & $-7.80 \pm 3.89$ & $0.26$ & $1.18 \pm 0.65$ & $1.48$ \\ [0.5em]
		       & BCES Bisector  	    & $-22.25 \pm 0.20$ & $-5.87 \pm 2.06$ & $0.26$ & $-$ & $1.16$ \\
		       & mFITEXY Bisector	    & $-22.18 \pm 0.20$ & $-4.34 \pm 0.84$ & $0.26$ & $-$ & $0.96$ \\
		       & {\tt linmix\_err} Bisector & $-22.19 \pm 0.25$ & $-3.83 \pm 1.39$ & $0.26$ & $-$ & $0.91$ \\ [1.0em]

@@

 Elliptical (E) (30)	& BCES $(Y|X)$  	     & $8.80 \pm 0.53$ & $-18.16 \pm 53.99$ & $0.76$ & $-$ & $3.02$ \\
 			& mFITEXY $(Y|X)$	     & $8.90 \pm 0.10$ & $4.47 \pm 0.88$ & $0.76$ & $0.29^{+0.14}_{-0.10}$ & $0.56$ \\
 			& {\tt linmix\_err} $(Y|X)$  & $8.84 \pm 0.12$ & $3.56 \pm 1.35$ & $0.76$ & $0.44 \pm 0.12$ & $0.59$ \\ [0.5em]
 			& BCES $(X|Y)$  	     & $8.80 \pm 0.18$ & $8.00 \pm 2.55$ & $0.76$ & $-$ & $1.01$ \\
 			& mFITEXY $(X|Y)$	     & $8.92 \pm 0.15$ & $6.85 \pm 1.75$ & $0.76$ & $0.36^{+0.20}_{-0.15}$ & $0.89$ \\
 			& {\tt linmix\_err} $(X|Y)$  & $8.89 \pm 0.20$ & $6.96 \pm 2.49$ & $0.76$ & $0.63 \pm 0.30$ & $0.89$ \\ [0.5em]
 			& BCES Bisector 	     & $8.80 \pm 0.11$ & $-0.03 \pm 0.10$ & $0.76$ & $-$ & $0.64$ \\
 			& mFITEXY Bisector	     & $8.91 \pm 0.13$ & $5.42 \pm 0.85$ & $0.76$ & $-$ & $0.73$ \\
 			& {\tt linmix\_err} Bisector & $8.85 \pm 0.16$ & $4.73 \pm 1.30$ & $0.76$ & $-$ & $0.67$ \\ [0.5em]

 Lenticular (S0) (11)	& BCES $(Y|X)$  	     & $7.75 \pm 0.58$ & $-11.51 \pm 31.78$ & $0.33$ & $-$ & $2.11$ \\
 			& mFITEXY $(Y|X)$	     & $7.65 \pm 0.12$ & $3.78 \pm 1.20$ & $0.33$ & $0.00^{+0.00}_{-0.00}$ & $0.26$ \\
 			& {\tt linmix\_err} $(Y|X)$  & $$ & $$ & $0.33$ & $$ & $$ \\ [0.5em]
 			& BCES $(X|Y)$  	     & $7.75 \pm 0.13$ & $3.54 \pm 0.99$ & $0.33$ & $-$ & $0.46$ \\
 			& mFITEXY $(X|Y)$	     & $7.65 \pm 0.12$ & $3.78 \pm 1.20$ & $0.33$ & $0.00^{+0.00}_{-0.00}$ & $0.49$ \\
 			& {\tt linmix\_err} $(X|Y)$  & $$ & $$ & $0.33$ & $$ & $$ \\ [0.5em]
 			& BCES Bisector 	     & $7.75 \pm 0.13$ & $-0.09 \pm 0.15$ & $0.33$ & $-$ & $0.48$ \\
 			& mFITEXY Bisector	     & $7.65 \pm 0.12$ & $3.78 \pm 0.85$ & $0.33$ & $-$ & $0.49$ \\
 			& {\tt linmix\_err} Bisector & $$ & $$ & $0.33$ & $-$ & $$ \\ [0.5em]
